\section{References}
\label{sec:references}

\begin{thebibliography}{10}

\bibitem{bobick2001}
A.~F. Bobick and J.~W. Davis, ``The recognition of human movement using temporal templates,'' \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol.~23, no.~3, pp. 257--267, 2001.


\bibitem{cover1967nearest}
T. M. Cover and P. E. Hart, ``Nearest Neighbor Pattern Classification,’’ \emph{IEEE Transactions on Information Theory}, vol. 13, no. 1, pp. 21–27, 1967.

\bibitem{ming2009hu}
H. Ming-Kuei, ``Visual pattern recognition by moment invariants,’’ \emph{IRE Transactions on Information Theory}, vol. 8, no. 2, pp. 179–187, 1962.

\bibitem{dalal2005}
N.~Dalal and B.~Triggs, ``Histograms of oriented gradients for human detection,'' in \emph{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2005, pp. 886--893.

\bibitem{scholkopf2002}
B.~Sch{\"o}lkopf and A.~J. Smola, \emph{Learning with Kernels}.\hskip 1em plus 0.5em minus 0.4em\relax MIT Press, 2002.

\bibitem{schuldt2004recognizing}
C. Schuldt, I. Laptev, and B. Caputo,``Recognizing human actions: A local SVM approach,''in \emph{Proc. IEEE International Conference on Pattern Recognition (ICPR)},2004.

\bibitem{hu1962}
M.-K. Hu,``Visual pattern recognition by moment invariants,''\emph{IRE Transactions on Information Theory},vol.~8, no.~2, pp.~179--187, 1962.

\bibitem{klaser2008}A. Kläser, M. Marszalek, and C. Schmid,``A spatio-temporal descriptor based on 3D-gradients,’’in \emph{Proc. British Machine Vision Conference (BMVC)}, 2008.

\bibitem{yang2007evaluating}
W. Yang, Y. Wang, and G. Mori,``Evaluating temporal information in human action recognition,''in \emph{Proc. IEEE International Conference on Computer Vision (ICCV)},2007.


\bibitem{klaser2008}
A.~Klaser, M.~Marsza{\l}ek, and C.~Schmid, ``A spatio-temporal descriptor based on 3D-gradients,'' in \emph{British Machine Vision Conference (BMVC)}, 2008.

\bibitem{simonyan2014twostream}
K. Simonyan and A. Zisserman,``Two-stream convolutional networks for action recognition in videos,''in \emph{Proc. Advances in Neural Information Processing Systems (NeurIPS)}, 2014.

\bibitem{cortes1995support}
C. Cortes and V. Vapnik,``Support-vector networks,’’ \emph{Machine Learning}, vol. 20, pp. 273–297, 1995.

\bibitem{rumelhart1986learning}
D. E. Rumelhart, G. E. Hinton, and R. J. Williams,``Learning representations by back-propagating errors,’’ \emph{Nature}, vol. 323, pp. 533–536, 1986.

\bibitem{ji2013cnn}
S. Ji, W. Xu, M. Yang, and K. Yu,``3D convolutional neural networks for human action recognition,''\emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol.~35, no.~1, pp.~221--231, 2013.

\end{thebibliography}
